Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-16 Draft/definition.tex
processes and definiton

\begin{figure*}[t]
\begin{center}
          \includegraphics[width=0.30\linewidth]{feynman/LO_EW_5}
          \raisebox{.5ex}{\includegraphics[width=0.35\linewidth]{feynman/LO_EW_2}}
          \raisebox{-1.8ex}{\includegraphics[width=0.32\linewidth]{feynman/LO_EW_3}}
\end{center}
        \caption{Sample tree-level diagrams that contribute to the process $\Pp\Pp\to\mu^+\nu_\mu\Pe^+\nu_{\Pe}\Pj\Pj$ at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
        In addition to typical VBS contribution (left), this order also possesses $s$-channel (middle) and tri-boson contributions (right). \AK{The text here is in conflict with the main text. Reading this it looks as if s-channel and tri-boson production are two different classifications, but in the main text we say both decay chains and tri-boson production belongs to s-channel.}}
\label{diag:LO}
\end{figure*}

>>>>

\begin{figure*}[t]
\begin{center}
          \includegraphics[width=0.30\linewidth]{feynman/LO_EW_5}
          \raisebox{.5ex}{\includegraphics[width=0.35\linewidth]{feynman/LO_EW_2}}
          \raisebox{-1.8ex}{\includegraphics[width=0.32\linewidth]{feynman/LO_EW_3}}
\end{center}
        \caption{Sample tree-level diagrams that contribute to the process $\Pp\Pp\to\mu^+\nu_\mu\Pe^+\nu_{\Pe}\Pj\Pj$ at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
        In addition to typical VBS contribution (left), this order also possesses $s$-channel contributions such as decay chain (middle) and tri-boson contributions (right).}
\label{diag:LO}
\end{figure*}

### 2018-02-16 Draft/process.tex
processes and definiton

As mentioned previously, the contribution of main interest in our process is
the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex.
Therefore it is justified to approximate the full EW contributions simply by only these contributions which contain the $2\rightarrow 2$ scattering process as a subpart.
However, this set of contributions is not gauge invariant. In order to make it gauge invariant, one 
should perform an on-shell projection of the incoming and outgoing $\PW$ bosons \MZ{it is incoming and outgoing, right? in case modify what follows}.
Unfortunately, these momenta are space-like and thus a simple on-shell projection is not possible.
Instead, one can keep the $\PW$ boson legs connected to the external quark line off-shell while the ones connected to the final-state leptons, which are already time-like, are put on-shell.
Then the polarisation of the gauge boson is accommodated for following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
Such an approximation is usually called effective vector-boson approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.

A less crude approximation consists in considering all $t$- and $u$- diagrams and squaring them separately, neglecting interference contributions between the two.
These interferences are expected to be small in the VBS fiducial region, as they are both phase-space and colour suppressed~\cite{Oleari:2003tc}.
The $s$-channel squared diagrams and any interferences with $s$-channels are also discarded.
This approximation is often called $t$-/$u$- approximation, VBF, or even VBS approximation.
We will adopt the latter denomination in the following of the article.
Such an approximation is implemented at LO in the computer codes {\sc Bonsay} \AK{CITATIONS} and the {\sc Powheg-Box}~\cite{Alioli:2010xd}.
This approximation is gauge-invariant, which can be seen by considering that the two protons and therefore the two incoming quarks belong to two different, but otherwise identical, copies of the $SU \left(3\right)$ gauge group.

@@

All other codes ({\sc MG5\_aMC}, {\sc MoCaNLO+Recola}, {\sc PHANTOM}, and {\sc Whizard})\AK{CITATIONS} consider all contributions of order $\mathcal{O}{\left(\alpha^{6}\right)}$ as well as all possible interferences.
Note that the final $\PW$ boson can always be considered either on-shell or off-shell without affecting the previous discussion.
All the codes mentioned here are described in details in the following sub-section.

@@

A further refinement is to consider the full real contributions as well as part of the virtual.
In particular one can consider only one-loop amplitudes where there is no gluon exchange between the quarks and 
assuming a cancellation of the infrared (IR) poles. Such an approximation is implemented by {\sc MG5\_aMC}.

Finally, when considering the full one-loop amplitude of order $\mathcal{O}(g_{\rm s}^2 g^6)$ and its corresponding real QCD radiation, other contributions have to be added.
Indeed, in order to cancel all infrared (IR) divergences arising, also one-loop amplitudes of order $\mathcal{O}(g^8)$ of EW type and their corresponding QED radiations have to be included.
The full computation of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consists thus not only of QCD-type corrections but also of EW ones.\footnote{For more details, the reader is referred to Ref.~\cite{Biedermann:2017bss}.\AK{Do we need this footnote given that the next sentence gives the reference?}} 
Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.

In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
\begin{itemize}
    \item all $s$- and $t/u$-channel diagrams that lead to the considered final state are included;
    \item interferences between diagrams are included at LO;
    \item diagrams which do not feature two resonant vector bosons are included;
    \item the so-called non-factorisable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
        are included;
    \item EW corrections to the $\mathcal O (\alpha^5\alphas)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
        the  $\mathcal O (\alpha^6$) term.
\end{itemize}

>>>>

As mentioned previously, the contribution of main interest in our process is
the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex.
Therefore it is justified to approximate the full EW contributions simply by only these contributions which contain the $2\rightarrow 2$ scattering process as a subpart.
However, this set of contributions is not gauge invariant. In order to make it gauge invariant, one 
should perform an on-shell projection of the incoming and outgoing $\PW$ bosons.
Unfortunately, the former momenta are space-like and thus a simple on-shell projection is not possible.
Instead, one can keep the $\PW$ boson legs connected to the external quark line off-shell while the ones connected to the final-state leptons, which are already time-like, are put on-shell.
Then the polarisation of the gauge boson is accommodated for following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
Such an approximation is usually called effective vector-boson approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.

A less crude approximation consists in considering all $t$- and $u$- diagrams and squaring them separately, neglecting interference contributions between the two.
These interferences are expected to be small in the VBS fiducial region, as they are both phase-space and colour suppressed~\cite{Oleari:2003tc}.
The $s$-channel squared diagrams and any interferences with $s$-channels are also discarded.
This approximation is often called $t$-/$u$- approximation, VBF, or even VBS approximation.
We will adopt the latter denomination in the following of the article.
Such an approximation is implemented at LO in the computer codes {\sc Bonsay} \AK{CITATIONS} and the {\sc Powheg-Box}~\cite{Alioli:2010xd}.
This approximation is gauge-invariant, which can be seen by considering that the two protons and therefore the two incoming quarks belong to two different, but otherwise identical, copies of the SU(3) gauge group.

@@

All other codes ({\sc MG5\_aMC}, {\sc MoCaNLO+Recola}, {\sc PHANTOM}, and {\sc Whizard})\AK{CITATIONS} \MP{No ref. for MoCaNLO+Recola} consider all contributions of order $\mathcal{O}{\left(\alpha^{6}\right)}$ as well as all possible interferences.
Note that the final $\PW$ boson can always be considered either on-shell or off-shell without affecting the previous discussion.
All the codes mentioned here are described in details in the following sub-section.

@@

A further refinement is to consider the full real contributions as well as part of the virtual.
In particular one can consider only one-loop amplitudes where there is no gluon exchange between the quarks and 
assuming a cancellation of the infrared (IR) poles.
Such an approximation is implemented by {\sc MG5\_aMC}.
\MP{I think this is not a gauge invariant approximation. If not, this should be commented on.}

Finally, when considering the full one-loop amplitude of order $\mathcal{O}(g_{\rm s}^2 g^6)$ and its corresponding real QCD radiation, other contributions have to be added.
Indeed, in order to cancel all infrared (IR) divergences arising, also one-loop amplitudes of order $\mathcal{O}(g^8)$ of EW type and their corresponding QED radiations have to be included.
The full computation of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consists thus not only of QCD-type corrections but also of EW ones. 
Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.

In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
\begin{itemize}
    \item all $s$- and $t/u$-channel diagrams that lead to the considered final state are included;
    \item interferences between diagrams are included at LO;
    \item diagrams which do not feature two resonant vector bosons are included;
    \item the so-called non-factorisable (NF) QCD corrections, \emph{i.e.}\ the corrections where (real or virtual) gluons are exchanged between different quark lines,
        are included;
    \item EW corrections to the $\mathcal O (\alpha^5\alphas)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
        the  $\mathcal O (\alpha^6$) term.
\end{itemize}
